---
title: "MUSA 508 HW3"
author: "Hanpu Yao"
date: "2021/10/29"
output: html_document
---

1. Introduction

Predictive policing is an analytical way to forecast potential criminal activities based on related factors, such as location and time. Since public safety resources like policing are limited, it is wise to allocate these resources to where crimes most likely to happen. Machine learning as a powerful tool also makes a lot of contribution to predict crimes.

However, predictive policing is controversial even if it is useful. Due to the complexity of physical environment and psychological factors, the data we obtain from real world can not be perfectly complete. Furthermore, since each piece of crime data is collected when a crime is reported, those less severe crimes might not be noticed or reported. This will probably causes bias to data so that we only predict existing crime instead of potential ones. Bearing these constraints in mind, we should be more rational when building a model.

Broken Windows Theory states that visible signs of civil disorder, such as vandalism, graffiti and public drinking, create an urban environment that promotes even more crime and disorder (Wilson & Kelling, 1982). In this report, I try to build a model to predict motor vehicle thefts in Chicago based on Broken Windows Theory. The reason I choose moto vehicle theft is that it is more visible than other kinds of theft and more dependent on the environment than relatively random crimes like murder or attack.



0. Set up 
Load package and source
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = TRUE)
library(tidyverse)
library(sf)
library(RSocrata)
library(viridis)
library(spatstat)
library(raster)
library(spdep)
library(FNN)
library(grid)
library(gridExtra)
library(knitr)
library(kableExtra)
library(tidycensus)
# functions
root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

```

Import data
```{r}
policeDistricts <- 
  st_read("https://data.cityofchicago.org/api/geospatial/fthy-xz3r?method=export&format=GeoJSON") %>%
  st_transform('ESRI:102271') %>%
  dplyr::select(District = dist_num)
  
policeBeats <- 
  st_read("https://data.cityofchicago.org/api/geospatial/aerh-rz74?method=export&format=GeoJSON") %>%
  st_transform('ESRI:102271') %>%
  dplyr::select(District = beat_num)

bothPoliceUnits <- rbind(mutate(policeDistricts, Legend = "Police Districts"), 
                         mutate(policeBeats, Legend = "Police Beats"))

```


```{r}

autotheft <- 
  read.socrata("https://data.cityofchicago.org/Public-Safety/Crimes-2017/d62x-nvdr") %>% 
    filter(Primary.Type == "MOTOR VEHICLE THEFT" & Description == "AUTOMOBILE") %>%
    mutate(x = gsub("[()]", "", Location)) %>%  # [ab] means a or b 
    separate(x,into= c("Y","X"), sep=",") %>%
    mutate(X = as.numeric(X),Y = as.numeric(Y)) %>% 
    na.omit() %>%
    st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant")%>%
    st_transform('ESRI:102271') %>% 
    distinct()

chicagoBoundary <- 
  st_read(file.path(root.dir,"/Chapter5/chicagoBoundary.geojson")) %>%
  st_transform('ESRI:102271') 
```

```{r fig.width=6, fig.height=4}
# uses grid.arrange to organize indpendent plots
grid.arrange(ncol=2,
ggplot() + 
  geom_sf(data = chicagoBoundary) +
  geom_sf(data = autotheft, colour="red", size=0.1, show.legend = "point") +
  labs(title= "Auto vehicle thefts, Chicago - 2017") +
  mapTheme(title_size = 14),

ggplot() + 
  geom_sf(data = chicagoBoundary, fill = "grey40") +
  stat_density2d(data = data.frame(st_coordinates(autotheft)), 
                 aes(X, Y, fill = ..level.., alpha = ..level..),
                 size = 0.01, bins = 40, geom = 'polygon') +
  scale_fill_viridis() +
  scale_alpha(range = c(0.00, 0.35), guide = FALSE) +
  labs(title = "Density of Moto vehicle thefts") +
  mapTheme(title_size = 14) + theme(legend.position = "none"))
```

Create fishnet.
```{r}
fishnet <- 
  st_make_grid(chicagoBoundary,
               cellsize = 500, 
               square = T) %>%
  .[chicagoBoundary] %>%            # <- MDH Added
  st_sf() %>%
  mutate(uniqueID = rownames(.))
```

Aggregate points to fishnet
```{r}
## add a value of 1 to each crime, sum them with aggregate
crime_net =
  dplyr::select(autotheft) %>% 
  mutate(count = 1) %>% 
  aggregate(., fishnet, sum) %>%
  mutate(count = replace_na(count, 0),
         uniqueID = rownames(.),
         cvID = sample(round(nrow(fishnet) / 57), # to make 100 groups
                       size=nrow(fishnet), replace = TRUE))


ggplot() +
  geom_sf(data = crime_net, aes(fill = count), color = NA) +
  scale_fill_viridis() +
  labs(title = "Count of Moto vehicle thefts for the fishnet") +
  mapTheme()
```


```{r}
abandonCars <- 
  read.socrata("https://data.cityofchicago.org/Service-Requests/311-Service-Requests-Abandoned-Vehicles/3c9v-pnva") %>%
    mutate(year = substr(creation_date,1,4)) %>% filter(year == "2017") %>%
    dplyr::select(Y = latitude, X = longitude) %>%
    na.omit() %>%
    st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant") %>%
    st_transform(st_crs(fishnet)) %>%
    mutate(Legend = "Abandoned_Cars")
  
abandonBuildings <- 
  read.socrata("https://data.cityofchicago.org/Service-Requests/311-Service-Requests-Vacant-and-Abandoned-Building/7nii-7srd") %>%
    mutate(year = substr(date_service_request_was_received,1,4)) %>%  filter(year == "2017") %>%
    dplyr::select(Y = latitude, X = longitude) %>%
    na.omit() %>%
    st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant") %>%
    st_transform(st_crs(fishnet)) %>%
    mutate(Legend = "Abandoned_Buildings")

graffiti <- 
  read.socrata("https://data.cityofchicago.org/Service-Requests/311-Service-Requests-Graffiti-Removal-Historical/hec5-y4x5") %>%
    mutate(year = substr(creation_date,1,4)) %>% filter(year == "2017") %>%
    filter(where_is_the_graffiti_located_ %in% c("Front", "Rear", "Side")) %>%
    dplyr::select(Y = latitude, X = longitude) %>%
    na.omit() %>%
    st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant") %>%
    st_transform(st_crs(fishnet)) %>%
    mutate(Legend = "Graffiti")

streetLightsOut <- 
  read.socrata("https://data.cityofchicago.org/Service-Requests/311-Service-Requests-Street-Lights-All-Out/zuxi-7xem") %>%
    mutate(year = substr(creation_date,1,4)) %>% filter(year == "2017") %>%
    dplyr::select(Y = latitude, X = longitude) %>%
    na.omit() %>%
    st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant") %>%
    st_transform(st_crs(fishnet)) %>%
    mutate(Legend = "Street_Lights_Out")

sanitation <-
  read.socrata("https://data.cityofchicago.org/Service-Requests/311-Service-Requests-Sanitation-Code-Complaints-Hi/me59-5fac") %>%
    mutate(year = substr(creation_date,1,4)) %>% filter(year == "2017") %>%
    dplyr::select(Y = latitude, X = longitude) %>%
    na.omit() %>%
    st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant") %>%
    st_transform(st_crs(fishnet)) %>%
    mutate(Legend = "Sanitation")

liquorRetail <- 
  read.socrata("https://data.cityofchicago.org/resource/nrmj-3kcf.json") %>%  
    filter(business_activity == "Retail Sales of Packaged Liquor") %>%
    dplyr::select(Y = latitude, X = longitude) %>%
    na.omit() %>%
    st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant") %>%
    st_transform(st_crs(fishnet)) %>%
    mutate(Legend = "Liquor_Retail")

neighborhoods <- 
  st_read("https://raw.githubusercontent.com/blackmad/neighborhoods/master/chicago.geojson") %>%
  st_transform(st_crs(fishnet)) 
```

```{r}
garbagecarts <- 
  read.socrata("https://data.cityofchicago.org/Service-Requests/311-Service-Requests-Garbage-Carts-Historical/9ksk-na4q") %>%
    mutate(year = substr(creation_date,1,4)) %>%  filter(year == "2017") %>%
    dplyr::select(Y = latitude, X = longitude) %>%
    na.omit() %>%
    st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant") %>%
    st_transform(st_crs(fishnet)) %>%
    mutate(Legend = "Garbage_Carts")

policestation <- 
  read.socrata("https://data.cityofchicago.org/Public-Safety/Police-Stations/z8bn-74gv") %>%
    dplyr::select(Y = latitude, X = longitude) %>%
    na.omit() %>%
    st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant") %>%
    st_transform(st_crs(fishnet)) %>%
    mutate(Legend = "police_station")
```

```{r}
trafficCrash <- 
  read.socrata("https://data.cityofchicago.org/Transportation/Traffic-Crashes-Crashes/85ca-t3if") %>%
    mutate(year = substr(crash_date,1,4)) %>% filter(year == "2017") %>%
    dplyr::select(Y = latitude, X = longitude) %>%
    na.omit() %>%
    st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant") %>%
    st_transform(st_crs(fishnet)) %>%
    mutate(Legend = "trafficCrash")
```

```{r}
vars_net <- 
  rbind(abandonCars, abandonBuildings, graffiti, streetLightsOut, sanitation, liquorRetail, trafficCrash, policestation, garbagecarts) %>%
  st_join(., fishnet, join=st_within) %>%
  st_drop_geometry() %>%
  group_by(uniqueID, Legend) %>%
  summarize(count = n()) %>%
    full_join(fishnet) %>%
    spread(Legend, count, fill=0) %>%
    st_sf() %>%
    dplyr::select(-`<NA>`) %>%
    na.omit() %>%
    ungroup()

```

```{r fig.width=6, fig.height=4}
vars_net.long <- 
  gather(vars_net, Variable, value, -geometry, -uniqueID)

vars <- unique(vars_net.long$Variable)
mapList <- list()

for(i in vars){
  mapList[[i]] <- 
    ggplot() +
      geom_sf(data = filter(vars_net.long, Variable == i), aes(fill=value), colour=NA) +
      scale_fill_viridis(name="") +
      labs(title=i) +
      mapTheme()}

do.call(grid.arrange,c(mapList, ncol=3, top="Risk Factors by Fishnet"))
```
nearest neighbour 

```{r}
st_c <- st_coordinates
st_coid <- st_centroid

trafficCrash.nn =
        nn_function(na.omit(st_c(st_coid(vars_net))), na.omit(st_c(trafficCrash)),3)

vars_net <-
  vars_net %>%
    mutate(
      Abandoned_Buildings.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(abandonBuildings),3),
      Abandoned_Cars.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(abandonCars),3),
      Graffiti.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(graffiti),3),
      Liquor_Retail.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(liquorRetail),3),
      Street_Lights_Out.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(streetLightsOut),3),
      Sanitation.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(sanitation),3),
      garbagecarts.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(garbagecarts),3),
      policestation.nn =
        nn_function(st_c(st_coid(vars_net)), st_c(policestation),3),
      trafficCrash.nn =
       trafficCrash.nn)
```

```{r}
final_net <-
  left_join(crime_net, st_drop_geometry(vars_net), by="uniqueID") 

final_net <-
  st_centroid(final_net) %>%
    st_join(dplyr::select(neighborhoods, name)) %>%
    st_join(dplyr::select(policeDistricts, District)) %>%
      st_drop_geometry() %>%
      left_join(dplyr::select(final_net, geometry, uniqueID)) %>%
      st_sf() %>%
  na.omit()
```

```{r fig.width=6, fig.height=4}
vars_net.long.nn <- 
  dplyr::select(vars_net, ends_with(".nn")) %>%
    gather(Variable, value, -geometry)

vars <- unique(vars_net.long.nn$Variable)
mapList <- list()

for(i in vars){
  mapList[[i]] <- 
    ggplot() +
      geom_sf(data = filter(vars_net.long.nn, Variable == i), aes(fill=value), colour=NA) +
      scale_fill_viridis(name="") +
      labs(title=i) +
      mapTheme()}

do.call(grid.arrange,c(mapList, ncol = 3, top = "Nearest Neighbor risk Factors by Fishnet"))
```


```{r}
## {spdep} to make polygon to neighborhoods... 
final_net.nb <- poly2nb(as_Spatial(final_net), queen=TRUE)
## ... and neighborhoods to list of weigths
final_net.weights <- nb2listw(final_net.nb, style="W", zero.policy=TRUE)


# local Morans'I
local_morans <- localmoran(final_net$count, final_net.weights, zero.policy=TRUE) %>% 
  as.data.frame()

# join local Moran's I results to fishnet
final_net.localMorans <- 
  cbind(local_morans, as.data.frame(final_net)) %>% 
  st_sf() %>%
  dplyr::select(Abandoned_Cars_Count = Abandoned_Cars, 
                Local_Morans_I = Ii, 
                P_Value = `Pr(z != E(Ii))`) %>%
  mutate(Significant_Hotspots = ifelse(P_Value <= 0.001, 1, 0)) %>%
  gather(Variable, Value, -geometry)

vars.moran = unique(final_net.localMorans$Variable)
plots2 = list()
for(i in vars.moran){
  plots2[[i]] = ggplot() +
      geom_sf(data = filter(final_net.localMorans, Variable == i), 
              aes(fill = Value), colour=NA) +
      scale_fill_viridis(name="",option="C") +
      labs(title=i) +
      mapTheme(title_size = 14) + theme(legend.position="bottom")}
grid.arrange(grobs=plots2, ncol = 4, 
             top=textGrob("Local Morans I statistics", gp=gpar(fontsize=18)))
```

```{r fig.width=6, fig.height=12}
## important to drop the geometry from joining features

correlation.long <-
  st_drop_geometry(final_net) %>%
    dplyr::select(-uniqueID, -cvID,  -name, -District) %>%
    gather(Variable, Value, -count)

correlation.cor <-
  correlation.long %>%
    group_by(Variable) %>%
    summarize(correlation = cor(Value, count, use = "complete.obs"))
    
ggplot(correlation.long, aes(Value, count)) +
  geom_point(size = 0.1) +
  geom_text(data = correlation.cor, aes(label = paste("r =", round(correlation, 2))),
            x=-Inf, y=Inf, vjust = 1.5, hjust = -.1) +
  geom_smooth(method = "lm", se = FALSE, colour = "black") +
  facet_wrap(~Variable, ncol = 2, scales = "free") +
  labs(title = "Burglary count as a function of risk factors") +
  plotTheme()
```

```{r}
ggplot(final_net) +
  geom_histogram(aes(count),bins=40, color="black") +
  labs(title = "Histogram of theft count",
       subtitle = "San Francisco, 2018") +
  plotTheme()

```

```{r}
final_net <-
  final_net %>% 
  mutate(theft.isSig = 
           ifelse(localmoran(final_net$count, 
                             final_net.weights, zero.policy = TRUE)[,5] <= 0.0000001, 1, 0)) %>%
  mutate(theft.isSig.dist = 
           nn_function(st_coordinates(st_centroid(final_net)),
                       st_coordinates(st_centroid(
                         filter(final_net, theft.isSig == 1))), 1))
```


```{r}
reg.vars <- c("Abandoned_Buildings.nn", "Abandoned_Cars.nn", "Graffiti.nn", 
              "Liquor_Retail.nn", "Street_Lights_Out.nn", "Sanitation.nn", 
              "trafficCrash.nn","policestation.nn","garbagecarts.nn")

reg.ss.vars <- c("Abandoned_Buildings.nn", "Abandoned_Cars.nn", "Graffiti.nn", 
              "Liquor_Retail.nn", "Street_Lights_Out.nn", "Sanitation.nn", 
              "trafficCrash.nn","policestation.nn","garbagecarts.nn",
              "theft.isSig", "theft.isSig.dist")
```

```{r}
crossValidate0 <- function(dataset, id, dependentVariable, indVariables) {
  
  allPredictions <- data.frame()
  cvID_list <- unique(dataset[[id]])
  
  for (i in cvID_list) {
    
    thisFold <- i
    cat("This hold out fold is", thisFold, "\n")
    
    fold.train <- filter(dataset, dataset[[id]] != thisFold) %>% as.data.frame() %>% 
      dplyr::select(id, geometry, indVariables, dependentVariable)
    fold.test  <- filter(dataset, dataset[[id]] == thisFold) %>% as.data.frame() %>% 
      dplyr::select(id, geometry, indVariables, dependentVariable)
    
    regression <-
      glm(count ~ ., family = "poisson", 
          data = fold.train %>% 
            dplyr::select(-geometry, -id))
    
    thisPrediction <- 
      mutate(fold.test, Prediction = predict(regression, fold.test, type = "response"))
    
    allPredictions <-
      rbind(allPredictions, thisPrediction)
    
  }
  return(st_sf(allPredictions))
}
```

```{r}
is.na(final_net)

which(is.na(final_net))

length(final_net$Abandoned_Buildings.nn)

summary(final_net)
```

```{r}



reg.cv = crossValidate0(
    dataset = final_net,
    id = "cvID",                           
    dependentVariable = "count",
    indVariables = reg.vars) %>%
  dplyr::select(cvID , count, Prediction, geometry)
```


```{r}
## RUN REGRESSIONS
reg.cv <- crossValidate0(
  dataset = final_net,
  id = "cvID",
  dependentVariable = "count",
  indVariables = reg.vars) %>%
    dplyr::select(cvID = cvID, count, Prediction, geometry)

reg.ss.cv <- crossValidate0(
  dataset = final_net,
  id = "cvID",
  dependentVariable = "count",
  indVariables = reg.ss.vars) %>%
    dplyr::select(cvID = cvID, count, Prediction, geometry)
  
reg.spatialCV <- crossValidate0(
  dataset = final_net,
  id = "name",
  dependentVariable = "count",
  indVariables = reg.vars) %>%
    dplyr::select(cvID = name, count, Prediction, geometry)

reg.ss.spatialCV <- crossValidate0(
  dataset = final_net,
  id = "name",
  dependentVariable = "count",
  indVariables = reg.ss.vars) %>%
    dplyr::select(cvID = name, count, Prediction, geometry)
```




```{r}
reg.summary <- 
  rbind(
    mutate(reg.cv,           Error = Prediction - count,
                             Regression = "Random k-fold CV: Just Risk Factors"),
                             
    mutate(reg.ss.cv,        Error = Prediction - count,
                             Regression = "Random k-fold CV: Spatial Process"),
    
    mutate(reg.spatialCV,    Error = Prediction - count,
                             Regression = "Spatial LOGO-CV: Just Risk Factors"),
                             
    mutate(reg.ss.spatialCV, Error = Prediction - count,
                             Regression = "Spatial LOGO-CV: Spatial Process")) %>%
    st_sf() 
```

A small multiple map of model errors by random k-fold and spatial cross validation.
```{r}
error_by_reg_and_fold <- 
  reg.summary %>%
    group_by(Regression, cvID) %>% 
    summarize(Mean_Error = mean(Prediction - count, na.rm = T),
              MAE = mean(abs(Mean_Error), na.rm = T),
              SD_MAE = mean(abs(Mean_Error), na.rm = T)) %>%
  ungroup()

error_by_reg_and_fold %>%
  ggplot(aes(MAE)) + 
    geom_histogram(bins = 30, colour="black", fill = "#FDE725FF") +
    facet_wrap(~Regression) +  
    geom_vline(xintercept = 0) + scale_x_continuous(breaks = seq(0, 8, by = 1)) + 
    labs(title="Distribution of MAE", subtitle = "k-fold cross validation vs. LOGO-CV",
         x="Mean Absolute Error", y="Count") +
    plotTheme()
```


```{r}
st_drop_geometry(error_by_reg_and_fold) %>%
  group_by(Regression) %>% 
    summarize(Mean_MAE = round(mean(MAE), 2),
              SD_MAE = round(sd(MAE), 2)) %>%
  kable() %>%
    kable_styling("striped", full_width = F) %>%
    row_spec(2, color = "black", background = "#FDE725FF") %>%
    row_spec(4, color = "black", background = "#FDE725FF") 
```

```{r}
theftppp <- as.ppp(st_coordinates(autotheft), W = st_bbox(final_net))
theftKD.1000 <- spatstat.core::density.ppp(theftppp, 1000)
theftKD.1500 <- spatstat.core::density.ppp(theftppp, 1500)
theftKD.2000 <- spatstat.core::density.ppp(theftppp, 2000)
theftKD.df <- rbind(
  mutate(data.frame(rasterToPoints(mask(raster(theftKD.1000), as(neighborhoods, 'Spatial')))), Legend = "1000 Ft."),
  mutate(data.frame(rasterToPoints(mask(raster(theftKD.1500), as(neighborhoods, 'Spatial')))), Legend = "1500 Ft."),
  mutate(data.frame(rasterToPoints(mask(raster(theftKD.2000), as(neighborhoods, 'Spatial')))), Legend = "2000 Ft.")) 

theftKD.df$Legend <- factor(theftKD.df$Legend, levels = c("1000 Ft.", "1500 Ft.", "2000 Ft."))

ggplot(data=theftKD.df, aes(x=x, y=y)) +
  geom_raster(aes(fill=layer)) + 
  facet_wrap(~Legend) +
  coord_sf(crs=st_crs(final_net)) + 
  scale_fill_viridis(name="Density") +
  labs(title = "Kernel density with 3 different search radii") +
  mapTheme(title_size = 14)
```

A table of raw errors by race context for a random k-fold vs. spatial cross validation regression.

```{r}
census_api_key("e79f3706b6d61249968c6ce88794f6f556e5bf3d", overwrite = TRUE)

tracts18 <- 
  get_acs(geography = "tract", variables = c("B01001_001E","B01001A_001E"), 
          year = 2018, state=17, county=031, geometry=T) %>%
  st_transform('ESRI:102271')  %>% 
  dplyr::select(variable, estimate, GEOID) %>%
  spread(variable, estimate) %>%
  rename(TotalPop = B01001_001,
         NumberWhites = B01001A_001) %>%
  mutate(percentWhite = NumberWhites / TotalPop,
         raceContext = ifelse(percentWhite > .5, "Majority_White", "Majority_Non_White")) %>%
  .[neighborhoods,]
```

```{r}
reg.summary <- 
  rbind(
    mutate(reg.cv,           Error = Prediction - count,
                             Regression = "Random k-fold CV: Just Risk Factors"),
                             
    mutate(reg.ss.cv,        Error = Prediction - count,
                             Regression = "Random k-fold CV: Spatial Process"),
    
    mutate(reg.spatialCV,    Error = Prediction - count,
                             Regression = "Spatial LOGO-CV: Just Risk Factors"),
                             
    mutate(reg.ss.spatialCV, Error = Prediction - count,
                             Regression = "Spatial LOGO-CV: Spatial Process")) %>%
    st_sf() 
```

```{r}
reg.summary %>% 
  filter(str_detect(Regression, "LOGO")) %>%
    st_centroid() %>%
    st_join(tracts18) %>%
    na.omit() %>%
      st_drop_geometry() %>%
      group_by(Regression, raceContext) %>%
      summarize(mean.Error = mean(Error, na.rm = T)) %>%
      spread(raceContext, mean.Error) %>%
      kable(caption = "Mean Error by neighborhood racial context") %>%
        kable_styling("striped", full_width = F)  
```

```{r}
theft_ppp <- as.ppp(st_coordinates(autotheft), W = st_bbox(final_net))
theft_KD <- spatstat.core::density.ppp(theft_ppp, 1000)

as.data.frame(theft_KD) %>%
  st_as_sf(coords = c("x", "y"), crs = st_crs(final_net)) %>%
  aggregate(., final_net, mean) %>%
   ggplot() +
     geom_sf(aes(fill=value)) +
     geom_sf(data = sample_n(autotheft, 1500), size = .5,colour = "red" , alpha = .2) +
     scale_fill_viridis(name = "Density") +
     labs(title = "Kernel density of 2017 burglaries") +
     mapTheme()
```

```{r}
autotheft18 <- 
  read.socrata("https://data.cityofchicago.org/Public-Safety/Crimes-2018/3i3m-jwuy") %>% 
  filter(Primary.Type == "MOTOR VEHICLE THEFT" & Description == "AUTOMOBILE") %>%
  mutate(x = gsub("[()]", "", Location)) %>%  # [ab] means a or b 
  separate(x,into= c("Y","X"), sep=",") %>%
  mutate(X = as.numeric(X),Y = as.numeric(Y)) %>% 
  na.omit() %>%
  st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant")%>%
  st_transform('ESRI:102271') %>% 
  distinct() %>%
  .[fishnet,]

```

```{r}
theft_KDE_sf <- as.data.frame(theft_KD) %>%
  st_as_sf(coords = c("x", "y"), crs = st_crs(final_net)) %>%
  aggregate(., final_net, mean) %>%
  mutate(label = "Kernel Density",
         Risk_Category = ntile(value, 100),
         Risk_Category = case_when(
           Risk_Category >= 90 ~ "90% to 100%",
           Risk_Category >= 70 & Risk_Category <= 89 ~ "70% to 89%",
           Risk_Category >= 50 & Risk_Category <= 69 ~ "50% to 69%",
           Risk_Category >= 30 & Risk_Category <= 49 ~ "30% to 49%",
           Risk_Category >= 1 & Risk_Category <= 29 ~ "1% to 29%")) %>%
  cbind(
    aggregate(
      dplyr::select(autotheft18) %>% mutate(theftCount = 1), ., sum) %>%
    mutate(theftCount = replace_na(theftCount, 0))) %>%
  dplyr::select(label, Risk_Category, theftCount)

theft_risk_sf <-
  filter(reg.summary, Regression == "Spatial LOGO-CV: Spatial Process") %>%
  mutate(label = "Risk Predictions",
         Risk_Category = ntile(Prediction, 100),
         Risk_Category = case_when(
           Risk_Category >= 90 ~ "90% to 100%",
           Risk_Category >= 70 & Risk_Category <= 89 ~ "70% to 89%",
           Risk_Category >= 50 & Risk_Category <= 69 ~ "50% to 69%",
           Risk_Category >= 30 & Risk_Category <= 49 ~ "30% to 49%",
           Risk_Category >= 1 & Risk_Category <= 29 ~ "1% to 29%")) %>%
  cbind(
    aggregate(
      dplyr::select(autotheft18) %>% mutate(theftCount = 1), ., sum) %>%
      mutate(theftCount = replace_na(theftCount, 0))) %>%
  dplyr::select(label,Risk_Category, theftCount)

```

```{r}


rbind(theft_KDE_sf, theft_risk_sf) %>%
  na.omit() %>%
  gather(Variable, Value, -label, -Risk_Category, -geometry) %>%
  ggplot() +
    geom_sf(aes(fill = Risk_Category), colour = NA) +
    geom_sf(data = sample_n(autotheft18, 3000), size = .3, colour = "black") +
    facet_wrap(~label, ) +
    scale_fill_viridis(discrete = TRUE) +
    labs(title="Comparison of Kernel Density and Risk Predictions",
         subtitle="2017 burglar risk predictions; 2018 burglaries") +
    mapTheme()
```


```{r}
rbind(theft_KDE_sf, theft_risk_sf) %>%
  na.omit() %>%
  gather(Variable, Value, -label, -Risk_Category, -geometry) %>%
  ggplot() +
    geom_sf(aes(fill = Risk_Category), colour = NA) +
    geom_sf(data = sample_n(burglaries18, 3000), size = .5, colour = "black") +
    facet_wrap(~label, ) +
    scale_fill_viridis(discrete = TRUE) +
    labs(title="Comparison of Kernel Density and Risk Predictions",
         subtitle="2017 burglar risk predictions; 2018 burglaries") +
    mapTheme()
```


```{r}
rbind(theft_KDE_sf, theft_risk_sf) %>%
  st_set_geometry(NULL) %>% na.omit() %>%
  gather(Variable, Value, -label, -Risk_Category) %>%
  group_by(label, Risk_Category) %>%
  summarize(count = sum(Value)) %>%
  ungroup() %>%
  group_by(label) %>%
  mutate(Rate_of_test_set_crimes = count / sum(count)) %>%
    ggplot(aes(Risk_Category,Rate_of_test_set_crimes)) +
      geom_bar(aes(fill=label), position="dodge", stat="identity") +
      scale_fill_viridis(discrete = TRUE) +
      labs(title = "Risk prediction vs. Kernel density, 2018 burglaries") +
      plotTheme() + theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
```

                